\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{paracol}
\usepackage{bookmark}
\usepackage{multicol}
\hypersetup{colorlinks=true,linkcolor=blue,filecolor=magenta,urlcolor=cyan,pdftitle={Overleaf Example},pdfpagemode=FullScreen,}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Gabriel Appau Abeyie} % Your name
\address{Cherokee Mills
2280 Sutherland Ave., Suite 228
Knoxville, TN 37919} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{Tel: (+1) 940-368-0576 \\ Email: gabeyie@vols.utk.edu \\ Web: \href{https://sites.google.com/view/gabrielabeyie/home}{Gabriel Abeyie}} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
%--copy and paste this region  if you need more--
\textbf{University of Tennessee}, Knoxville.{\hfill{Aug 2020 - May 2025}\\}
{\sl Doctor of Philosophy (Ph.D)}, Economics\\
    
\textbf{University of North Texas}, Denton.{\hfill{Aug 2018 - May 2020}\\}
{\sl Master of Science (MS)}, Economics\\
    
\textbf{University of Ghana}, Accra, Ghana.{\hfill{Aug 2013 - May 2017}\\}
{\sl Bachelor of Arts (BA)}, Economics \& Statistics, Double Major.\\
%--copy and paste this region  if you need more--
\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH INTEREST
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Interests}
\normalfont{\textbullet{ Macroeconomics}}\\
\normalfont{\textbullet{ Time Series Forecasting}}\\
\normalfont{\textbullet{ Machine Learning}}\\
\normalfont{\textbullet{ International Finance}}\\
\end{rSection}

%--------------------------------------------------------------------------------
%    RESEARCH
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Research}
    %--copy and paste this region  if you need more--
    {\bf \underbar{Job Market Paper}}\\
    Identifying Oil Supply News Shocks: The Impact of OPEC Announcements Using Textual Data\\\\
    {\bf \underbar{Working Paper}}\\
    Beyond News Headlines and TF-IDF: Enhancing Text-Based Forecasting Models with Validated Collocations and Improved Attention.
    (\textbf{R\&R at International Journal of Forecasting})\\
    \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4822767#:~:text=This%20paper%20proposes%20a%20method%20for}{Working Paper Version}\\\\
    {\bf \underbar{Works In Progress}}\\
    \normalfont{\textbullet{ Forecasting Crude Oil Price Returns: A Principal Weighted-Elastic Net (PW-EN) Approach (with Andrew Hanson)}}\\
    \normalfont{\textbullet{ Welfare Implications of Bubble Dynamics (with Andrew Hanson)}}\\
    \normalfont{\textbullet{ A Regularized Scaled-Sliced Inverse Regression (REGs-SIR) for High Dimensional Data}}\\
    \normalfont{\textbullet{The Role of Expert Opinion and Analysis in the Crude Oil Market}}\\
    %--copy and paste this region  if you need more--
    \end{rSection}

%--------------------------------------------------------------------------------
%    TEACHING
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Teaching}

    \textbf{Independent Instructor \hfill{Aug 2022 - Dec 2022}\\}
    \normalfont{University of Tennessee, \textit{Principles of Macroeconomics} (4.1/5 Evaluation)\\}
    \normalfont{\textbullet{ Instructed a class of 100 undergraduate students.}}\\
    \normalfont{\textbullet{ Developed course lectures, assignments, and quizzes.}}\\
    \normalfont{\textbullet{ Graded assignments and held regular office hours.}}\\
    
    \textbf{Teaching Fellow (Independent Instructor) \hfill{Jan 2020 - May 2020}\\}
    \normalfont{University of North Texas, \textit{Principles of Macroeconomics} (4.6/5 Evaluation)\\}
    \normalfont{\textbullet{ Led a class of 47 undergraduate students.}}\\
    \normalfont{\textbullet{ Created lecture materials, assignments, and assessments.}}\\
    \normalfont{\textbullet{ Graded coursework and maintained regular office hours.}}\\

    \textbf{Teaching Fellow (Independent Instructor) \hfill{Aug 2019 - Dec 2019}\\}
    \normalfont{University of North Texas, \textit{Principles of Macroeconomics} (3.9/5 Evaluation)\\}
    \normalfont{\textbullet{ Taught a class of 48 undergraduate students.}}\\
    \normalfont{\textbullet{ Prepared lecture content and evaluated student performance.}}\\
    \normalfont{\textbullet{ Graded assignments and held regular office hours.}}\\

    \textbf{Graduate Teaching Assistant/Recitation Instructor \hfill{Jan 2020 - May 2020}\\}
    \normalfont{University of North Texas, \textit{Advanced Econometrics} (PhD coursework)\\}
    \normalfont{\textbullet{ Conducted tutorial sessions for first-year PhD students.}}\\
    \normalfont{\textbullet{ Graded assignments and managed course grading.}}\\

    \textbf{Graduate Teaching Assistant/Recitation Instructor \hfill{Aug 2019 - Dec 2019}\\}
    \normalfont{University of North Texas, \textit{Mathematical Economics} (PhD coursework)\\}
    \normalfont{\textbullet{ Led tutorial sessions for first-year PhD students.}}\\
    \normalfont{\textbullet{ Assisted with homework preparation and grading.}}\\
    \normalfont{\textbullet{ Managed course grading records.}}\\

    \textbf{Graduate Teaching Assistant \hfill{Jan 2019 - May 2019}\\}
    \normalfont{University of North Texas, \textit{Public Economics}\\}
    \normalfont{\textbullet{ Assisted students with homework and exam preparation.}}\\

    \textbf{Academic Assistant \hfill{Aug 2018 - July 2019}\\}
    \normalfont{University of North Texas, \textit{Principles of Microeconomics \& Macroeconomics}\\}
    \normalfont{\textbullet{ Provided homework and exam assistance to students.}}\\
    \normalfont{\textbullet{ Graded assignments and quizzes.}}\\
    \normalfont{\textbullet{ Monitored exams and maintained grading records.}}\\

\end{rSection}

\begin{rSection}{Presentations}
\textbf{University of Tennessee}, Knoxville., Economics Brown Bag Seminar Series{\hfill{Fall 2021}\\}
{\sl Welfare Implcations of Bubble Dynamics}\\\\
\textbf{Southern Econ. Assoc.}, 92nd Annual Conference, Fort Lauderdale, FL.{\hfill{November 19-21, 2022}\\}
{\sl Welfare Implcations of Bubble Dynamics}\\\\
\textbf{University of Tennessee}, Knoxville., Economics Brown Bag Seminar Series{\hfill{Fall 2023}\\}
{\sl Identifying Oil Supply News Shocks: The Impact of OPEC Announcements Using Textual Data}\\\\
\textbf{University of Tennessee}, Knoxville., Economics Brown Bag Seminar Series{\hfill{Fall 2024}\\}
{\sl Forecasting Crude Oil Price Returns: A Principal Weighted-Elastic Net (PW-EN) Approach}\\\\
\textbf{Southern Econ. Assoc.}, 94th Annual Conference, Washington, DC.{\hfill{November 23-25, 2024}\\}
{\sl 1. Identifying Oil Supply News Shocks: The Impact of OPEC Announcements Using Textual Data\\
2.Beyond News Headlines and TF-IDF: Enhancing Text-Based Forecasting Models with Validated Collocations and Improved Attention.}\\
\end{rSection}

\begin{rSection}{Awards and Scholarships} 

    \textbf{Aaron Wuensch Memorial Scholarship\\for the Top Graduate Student Award  \hfill April 2019}\\
    University of North Texas, Department of Economics.
        
    \textbf{J. Fred and Wilma Holly Fellowship} {\hfill{\bf Aug 2020 - May 2025}\\}
     University of Tennessee, Department of Economics.
        
    \textbf{Texas Public Education Grant (TPEG) \hfill Aug 2019}\\
    Division of International Affairs, University of North Texas.
        
    \textbf{Toulouse Graduate Scholarship \hfill Aug 2019}\\
    Toulouse Graduate School, University of North Texas.
        
    \textbf{Mary D. Walsh Endowed Scholarship \hfill April 2019}\\
    Toulouse Graduate School, University of North Texas.
        
    \textbf{Toulouse Graduate Scholarship \hfill Jan 2019}\\
    Toulouse Graduate School, University of North Texas.
        
    \end{rSection}

\begin{rSection}{Skills}
    \textbf{Programming Languages:} Python, R, MATLAB, Stata
    \end{rSection}

\begin{rSection}{Memberships}
    \normalfont{\textbullet{ American Economic Association}}\\
    \normalfont{\textbullet{ International Institute of Forecasters}}\\
    \normalfont{\textbullet{ Southern Economic Association}}\\
    \end{rSection}

\begin{rSection}{References} 

    \begin{multicols}{3}
        \textbf{Andrew S. Hanson, PhD}\\
        Department of Economics\\
        University of Tennessee, KN\\
        ahanson@utk.edu
        
        \columnbreak
        
        \textbf{Luiz R. Lima, PhD}\\
        Department of Economics\\
        University of Tennessee, KN\\
        llima@utk.edu
        
        \columnbreak
        
        \textbf{Mohammed Mohsin, PhD}\\
        Department of Economics\\
        University of Tennessee, KN\\
        mmohsin@utk.edu
    \end{multicols}
        
\end{rSection}

\end{document}